Explaining probabilistic prediction on the simplex with Shapley compositions

### 2023-12-19 paper/main.tex
edit paper

\subsubsection{More classes}
\label{sec:moreclasses}
When there are more classes, all the dimension of the ILR space cannot be visualized at once but $2$ or $3$-dimensional subspaces can still be visualized. However, in order to choose which ILR components to visualize, one needs to understand what they refer too. The next section provides some intuition about that in the context of the explanation of a classifier prediction with more than 4 classes.

>>>>

\subsubsection{More classes}
\label{sec:moreclasses}
When there are more classes, all the dimension of the ILR space cannot be visualized at once but $2$ or $3$-dimensional subspaces can still be visualized. However, in order to choose which ILR components to visualize, one needs to understand what they refer to. For this purpose, the next section discusses the interpretation of the ILR components in more details in the context of the explanation of a classifier prediction with more than 4 classes.
